---
title: newsfeed
output: github_document
---

```{r, include = FALSE}
knitr::opts_knit$set(
  root.dir = file.path(Sys.getenv("HOME"), "github")
)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

Compile NEWS files from several packages

## Install and load

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

if (!requireNamespace("newsfeed", quietly = TRUE))
    BiocManager::install("waldronlab/newsfeed")

library(newsfeed)
```

## Optional packages

* clipr - allows the user to send the collection of NEWS files to the clipboard
* rmarkdown - when `render = TRUE` in `collect`, the package will show an HTML
page of NEWS updates

## Moving to the base packages directory

Users should move one level up from the package directory to be able
to find the NEWS files in the package:

```{r,eval=FALSE}
setwd("..")
```

In this case, when compiling the `Rmd` file, I move one level up.

## Compiling NEWS files

```{r}
collect("newsfeed", render = FALSE)
```

## Reading the NEWS

Here is how the NEWS collection would look if all NEWS files were written
in `NEWS.md` format:

```{r,results="asis",echo=FALSE}
cat(readLines(
    collect("newsfeed", render = TRUE, raw = TRUE)
))
```
